Data Preparation

### 2021-07-21 x0_data-preparation.Rmd
Geschafft!!

prep_base_data <- function(.fn = file_names, ...){
ds <- read_osn_covid(.fn)
ds <- ds %>% append_ad_ctry() 
ds <- ds %>% append_region()

@@

@@

# crunch study data
walk(fns, .f = prep_base_data)
```

>>>>

prep_base_data <- function(.fn = file_names, ...){

ds <- read_osn_covid(.fn)
ds <- ds %>% append_ad_ctry() 
ds <- ds %>% append_region()

@@

#----------------------- geo referencing of lat-lon to complement ADEP/ADES
eez_land <- load_shapefile_for_geo_ref()

@@

# crunch study data
walk(fns, .f = prep_base_data)
walk(fns[13:length(fns)], .f = prep_base_data)
```
